Resource Buying Games

### 2017-02-24 paper.tex
matroids in paper write up

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage[framed]{ntheorem}

@@

@@

\begin{document}
\maketitle

\begin{defi}[Marginally non-increasing]
  Whoop
\end{defi}

>>>>

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage{todo}
\usepackage[framed]{ntheorem}

@@

\newcommand{\tupel}[1]{\left(#1\right)}
\newcommand{\set}[1]{\left\{#1\right\}}

@@

\begin{document}
\input{tikz/settings}
\maketitle
\section{Introduction}

\section{Matroids}
In this section we present the combinatorial structure of Matroids.
\todo{why matroids?}

We use matroids as a generalisation of the concept of linear independence.
Matroids can be defined as a ground-set and the family of linear
independent sets of this ground-set. This family has to satisfy three
properties, i.e.
\begin{enumerate}
  \item the empty set is linear independent,
  \item all subset of a linear independent set are linear independent and
  \item for two linear independent sets we can find an element of the larger
    set that forms a linear independent set when added to the smaller set.
\end{enumerate}
We use an equivalent definition of matroids which in a way captures the idea of
having a vector space by giving instead of linear independent sets the bases of
the ground-set.
\begin{defi}
  The structure $\tupel{E, \mathcal{B}}$ with $\mathcal{B}\subseteq 2^{E}$ is
  a matroid if
  \begin{enumerate}
    \item $\mathcal{B}\neq\emptyset$
    \item let $B,B'\in\mathcal{B}$ and for every $x\in B$ there is $y\in B'$
      s. t. $(B\setminus\set{x})\cup\set{y}\in\mathcal{B}$
  \end{enumerate}
\end{defi}
In analogy to vector spaces we consider every element of a basis to open access
to a dimension. We illustrate this concept with the following example: given an
undirected connected graph $G = \tupel{V, E}$ we will argue that
$\tupel{E, \mathcal{S}}$ with $\mathcal{S}$ as edge-sets of spanning trees
in $G$ forms a matroid. In order to meet the requirement that $\mathcal{S}$
must not be empty we restrict $G$ to those graphs with at least two distinct
vertices. Furthermore, given two spanning trees $\tupel{V, S_{1}}$ and
$\tupel{V, S_{2}}$ of $G$ then removing an edge from $S_{1}$ yields a subgraph
of $G$ that is separated into two connected components. Since $S_{2}$ forms a
spanning tree as well there must be an edge connecting these components which
can be used to again obtain a spanning tree\footnote{see Figure
\ref{fig:spanning} for an illustration}. Consider the algorithm of Prim
which computes spanning trees by iteratively adding edges which do not close a
cycle: every added edge works towards a basis in $\mathcal{S}$ and opens a
dimensionality by connecting one of the graph nodes.
\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \node (t) {\input{tikz/graphp1}};
      \node[below left=of t] {\input{tikz/graphp1S1}};
      \node[below =of t] {\input{tikz/graphp1S2}};
      \node[below right=of t] {\input{tikz/graphp1S1}};
    \end{tikzpicture}
  \end{center}
  \caption{Graph with its spanning trees}
  \label{fig:spanning}
\end{figure}
\todo{working iteratively towards a basis by prim's algorithm as example to
introduce cuts and contractions and deletions}

\todos
